Bayesian non-parametric inference for multivariate peaks-over-threshold models

### 2024-02-08 conclusion.tex
init switch to entropy

Establishing the angular measure
    specifically in $\mathbb{S}_{\infty}^{d-1}$ provides two benefits over 
    $\mathbb{S}_p^{d-1}$.  First, the transformation to 
    $\mathbb{S}_{\infty}^{d-1}$ is unique.  Observe in 
    Equation~\eqref{eqn:pnormtinv}, establishing $y_d$ as a function
    of $y_1,\ldots,y_{d-1}$ can be replaced in form with any $y_{\ell}$, 
    indicating there are $d$ equivalent transformations, each yielding a different
    Jacobian and, for $p>1$, potentially resulting in a different calculated density.  
    Second, evaluation of geodesic distance on $\mathbb{S}_p^{d-1}$ is not 
    straightforward.  However, we have demonstrated a computationally efficient 
    upper bound on geodesic distance on $\mathbb{S}_{\infty}^{d-1}$.

@@

The computations in this paper were performed on a desktop computer with an 
    AMD Ryzen 5950X processor. The program is largely single-threaded, so 
    computation time is not dependent on available core count.  In each case, 
    we run the MCMC chain for 50\,000 iterations, with a burn-in of 40\,000 
    samples.  Fitting the PG--G model on the ERA5 dataset took approximately 
    15 minutes.  Work is in progress to optimize the code, and explore 
    parallelization where possible.  We are also exploring alternative 
    computational approaches that will make it feasible to tackle very high 
    dimensional problems, such as variational Bayes. In fact, to elaborate on 
    the study of IVT, there is a need to consider several hundreds, if not thousands, 
    of grid cells over the Pacific Ocean in order to obtain a good description of 
    atmospheric events responsible for large storm activity over California.

>>>>

Establishing the angular measure
    specifically in $\mathbb{S}_{\infty}^{d-1}$ provides two benefits over 
    $\mathbb{S}_p^{d-1}$.  First, the transformation to 
    $\mathbb{S}_{\infty}^{d-1}$ is unique.  Observe in 
    Equation~\eqref{eqn:pnormtinv}, establishing $y_d$ as a function
    of $y_1,\ldots,y_{d-1}$ can be replaced in form with any $y_{\ell}$, 
    indicating there are $d$ equivalent transformations, each yielding a different
    Jacobian and, for $p>1$, potentially resulting in a different calculated density.  
    Second, evaluation of geodesic distance on $\mathbb{S}_p^{d-1}$ is not 
    straightforward.  However, we have demonstrated a computationally efficient 
    upper bound on geodesic distance on $\mathbb{S}_{\infty}^{d-1}$.  Accepting
    these foibles, it would be interesting to explore the distribution on 
    $\mathbb{S}_{p}^{d-1}$,

@@

The computations in this paper were performed on a desktop computer with an 
    AMD Ryzen 5000 series processor. The program is largely single-threaded, so 
    computation time is not dependent on available core count.  In each case, 
    we run the MCMC chain for 50\,000 iterations, with a burn-in of 40\,000 
    samples.  Fitting the PG--G model on the ERA5 dataset took approximately 
    15 minutes.  Work is in progress to optimize the code, and explore 
    parallelization where possible.  We are also exploring alternative 
    computational approaches that will make it feasible to tackle very high 
    dimensional problems, such as variational Bayes. In fact, to elaborate on 
    the study of IVT, there is a need to consider several hundreds, if not thousands, 
    of grid cells over the Pacific Ocean in order to obtain a good description of 
    atmospheric events responsible for large storm activity over California.
